cleaning the pheno table

### 2020-11-12 scripts/37_clean_pheno_refreshed.Rmd
jesus how much time I spent on this

```{r}
library(tidyverse)
```

@@

  dt_CART_italy_samples = fread("/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/Set 81 Samples.txt")
  setnames(dt_CART_italy_samples,"pt_id","pid")
  setnames(dt_CART_italy_samples,"SampleID","sampleid")
  setnames(dt_CART_italy_samples,"OligoID","oligoid")

@@

all.equal(colnames(pw_all_or)[2:ncol(pw_all_or)], pheno_all$sampleid)
```
```{r}
pheno <- list(mitaly = pheno_mitaly,
              upenn = pheno_upenn,
              all = pheno_all)

>>>>

```{r}
library(tidyverse)
library(data.table)
```

@@

  dt_CART_italy_samples = fread("/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/samples/opbg_sampleskey_11092020_with_oligoid.csv")
  setnames(dt_CART_italy_samples,"pt_id","pid")
  #setnames(dt_CART_italy_samples,"SampleID","sampleid")
  #setnames(dt_CART_italy_samples,"OligoID","oligoid")

@@

all.equal(colnames(pw_all_or)[2:ncol(pw_all_or)], pheno_all$sampleid)

# only msk data
pheno_msk <-   msk %>% 
    select(sampleid, CR, Toxicity)

pheno_msk %>% 
  select( Toxicity) %>% 
            t %>% 
            write.table(str_glue('../data/lefse/msk__pheno_Toxicity.txt'), sep = '\t', quote = F, row.names = T, col.names = F)

pw_msk_or <- bind_cols(pw_msk[,1],pw_msk[,pheno_msk$sampleid]) 
all.equal(colnames(pw_msk_or)[2:ncol(pw_msk_or)], pheno_msk$sampleid)

pw_msk_or %>% 
  write_tsv(str_glue('../data/lefse/msk_cts.tsv'))
```
```{r}
pheno <- list(mitaly = pheno_mitaly,
              upenn = pheno_upenn,
              all = pheno_all)
